Verifying Demonstrations

### 2018-02-20 paper/ZKPK.tex
Adds description of how to make Schnorr malicious verifier ZK

>>>>

The Schnorr protocol in itself only provides honest-verifier zero-knowledge.
To achieve malicious-verifier zero-knowledge, we have to choose \(k\) (size of 
the challenge) logarithmic in the security parameter \(\lambda\) and repeat the 
protocol sufficiently many times (also logarithmic in the security parameter).
